NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-27 paper/pipeline.tex
updates on pipeline

There are many ways to update the model to correct a prediction. A simple way to achieve it is applying standard backpropagation that overfits to the example. However, without any constraint, the update step may alter the model in unexpected ways.
% \shusen{what is the benefit of using mira?}
Instead, we adopted the same idea in \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the amount of change to the parameter. Therefore, in the proposed tool, we minimize the combined loss function by the following:
\begin{equation}
\underset{w'}{\mathrm{argmin}}( C \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||^2)
\end{equation}
where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural model, $\mathbf{W}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the parameters to update, and $C$ is the weighting term, which determines whether we intended to emphasis more on obtaining better fitting or deviating less from the original model. Due to the nonconvex nature of the neural networks, we use SGD to optimize the above combined loss function.
%
Under this formation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.

>>>>

There are many ways to update the model to correct a prediction. A simple way to achieve it is applying standard backpropagation that overfits to the example. However, without any constraint, the update step may alter the model in unexpected ways.
% \shusen{what is the benefit of using mira?}
Instead, we adopt the same idea in \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003}, where we regulate the optimization with the amount of change to the parameter. Therefore, in the proposed tool, we minimize the combined loss function by the following:
\begin{equation}
\underset{w'}{\mathrm{argmin}}( C \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||^2)
\end{equation}
where $\mathbb{J}(\mathbf{W})$ is the loss function of the neural model, $\mathbf{W}$ is the original model's parameters taken as constant, $\mathbf{W}'$ is the parameters to update, and $C$ is the weighting term, which determines whether we intended to emphasis more on obtaining better fitting or deviating less from the original model. Due to the nonconvex nature of the neural networks, we use SGD to optimize the above combined loss function.
%
Under this formation, we try to find a good approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.
